Discrete Quantum Theories and Computing

### 2018-12-13 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

Since we as human cannot distinguish quantities differing only by
an arbitrarily small extent \cite{Turing_1937,Gisin2017}, quantum
mechanics and computation based on the continuum of complex numbers
may not capture our ability of predicting quantum phenomenon and the
power of quantum computation. Being agnostic about whether the reality
is ultimately discrete or continuous, we considered two types of models
to incorporate our limitation of distinguishability into quantum theories.
By assuming the quantum states are ultimately quantized and distinguishable,
the first type of our quantum theories replaces the complex numbers
by discrete finite fields. We then shift our attention to focus on
the limitation of distinguishability itself, incorporate the finite
precision measurement into our model, and consider quantum interval-valued
probability measures.

After first suggesting by Richard Feynman and 40 years theoretical
developments~\cite{Feynman1982Simulating}, IBM, Rigetti, Google,
Microsoft, and many other companies start to build realistic quantum
computers to simulate chemical molecules for drug development and
to improving the classical algorithms like artificial and machine
learning \cite{Shieber2018,Kahn2019}. Before we dive into the issue
between our limitation of distinguishability and quantum theories
and computing, it is instructive to review how classical physical
quantities are characterized and computed.

>>>>

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{italian}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

Since we as human cannot distinguish quantities differing only by
an arbitrarily small extent \cite{Turing_1937,Gisin2017}, quantum
mechanics and computation based on the continuum of complex numbers
may not capture our ability of predicting quantum phenomenon and the
power of quantum computation. Being agnostic about whether the reality
is ultimately discrete or continuous, we considered two types of quantum
models to incorporate our limitation of distinguishability. By assuming
the quantum states are ultimately quantized and distinguishable, our
first type of quantum theories replaces the complex numbers by discrete
finite fields. We then focus on the limitation of distinguishability
itself, incorporate the finite precision measurement into our model,
and consider quantum interval-valued probability measures.

After first suggesting by Richard Feynman 40 years ago~\cite{Feynman1982Simulating},
IBM, \textitalian{Rigetti}, Google, Microsoft, and many other companies
and countries start to build realistic quantum computers \cite{Shieber2018,Kahn2019},
and seek more efficient ways to simulate chemical molecules and to
break down RSA \cite{boneh1999twenty,wiki:RSAFactoring}. Despite
how we compute these two tasks, we can notice they require us to compute
two different types of quantities. While RSA requires discrete computation,
it is beyond our ability to distinguish whether the quantities required
by simulating molecules are discrete or not. Before discussing the
quantities characterizing and computing with quantum mechanics, it
is instructive to review how classical physical quantities are characterized
and computed.
